Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-13 thirdPaper/draft/typeConeAssociahedra.tex
typographic changes

\begin{lemma}\label{lemm::mesh mutations and meshes}
 The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
\end{lemma}
\begin{proof}
 If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
 \[
  X\to E\to X' \to \susp E,
 \]
 so that~$X' = \tau^{-1}X$.  Moreover, there is a slice of the Auslander--Reiten quiver of~$\cat$ containing~$X$ and all indecomposable direct factors of~$E$.  The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a sink, and mutation at~$X$ gives~$X'$.  Thus~$\{x,x'\}$ is in~$\meshes$.  This gives an injective map from the set of positive mutations to~$\meshes$.

 \smallskip

 Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.  Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a sink in~$T$ and mutation at~$X$ yields~$X'$.  Since~$X$ is a sink, the mutation triangle starting and ending in~$X$ are
 \[
  X\to E\to X' \to \susp X \quad \textrm{and} \quad  X' \to 0 \to X \to \susp X'.
 \]
  Therefore~$X' = \susp^{-1}X = \tau^{-1}X$.  Thus the first triangle is the almost-split triangle starting in~$X$.  Since the pair~$\{x,x'\}$ is not initial, the mutation is a positive mesh mutation.  This gives an injective map from~$\meshes$ to the set of positive mutations. 
\end{proof}

@@

\begin{remark}
Let~$\delta\in\mathbb{E}(Z,X)$ be an~$\mathbb{E}$-extension. By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X')\ \ \text{and}\ \ \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
For short, we write~$f_\ast\delta$ and~$h^\ast\delta$ instead.
Using those notations, we have, in~$\mathbb{E}(Z',X')$
\[ \mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta. \]
\end{remark}

@@

\begin{definition}
\label{DefSqEquiv}
Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
\[ X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \ \text{ and } \ X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z \]
are said to be \defn{equivalent} if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
\[
\xy
(-20,0)*+{X}="X";
(5,0)*+{}="1";
(0,6)*+{Y}="Y";
(0,-6)*+{Y'}="Y'";
(-5,0)*+{}="2";
(20,0)*+{Z}="Z";
%
{\ar^{x} "X";"Y"};
{\ar^{y} "Y";"Z"};
{\ar_{x^{\prime}} "X";"Y'"};
{\ar_{y^{\prime}} "Y'";"Z"};
%
{\ar^{g}_{\cong} "Y";"Y'"};
%
{\ar@{}|{} "X";"1"};
{\ar@{}|{} "2";"Z"};
\endxy
\]
The equivalence class of~$X \xrightarrow{x} Y \xrightarrow{y} Z$ is denoted by~$[X \xrightarrow{x} Y \xrightarrow{y} Z]$.
\end{definition}

@@

\begin{definition}(\cite[Def.~2.12]{NakaokaPalu})
A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an \defn{extriangulated category} if the following holds:
\begin{itemize}
\item[{\rm (ET1)}] $\mathbb{E}:\cat^{\mathrm{op}}\times\cat\to\mathit{Ab}$ is an additive bifunctor;
\item[{\rm (ET2)}] $\mathfrak{s}$ is an additive realization of~$\mathbb{E}$;
\item[{\rm (ET3)}] Let~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$ be~$\mathbb{E}$-extensions, respectively realized by~$X\xrightarrow{x}Y\xrightarrow{y}Z$ and~$X'\xrightarrow{x'}Y'\xrightarrow{y'}Z'$. Then, for any commutative square
\[
\xy
(-12,6)*+{X}="0";
(0,6)*+{Y}="2";
(12,6)*+{Z}="4";
%
(-12,-6)*+{X'}="10";
(0,-6)*+{Y'}="12";
(12,-6)*+{Z'}="14";
%
{\ar^{x} "0";"2"};
{\ar^{y} "2";"4"};
%
{\ar_{f} "0";"10"};
{\ar^{g} "2";"12"};
%
{\ar_{x'} "10";"12"};
{\ar_{y'} "12";"14"};
%
{\ar@{}|{} "0";"12"};
%
{\ar@{}|\circlearrowright "0";"12"};
\endxy 
\]
in~$\cat$, there exists a morphism~$(f,h):\delta\to\delta'$ satisfying~$h\circ y=y'\circ g$.
\item[{\rm (ET3)$^{\mathrm{op}}$}] Dual of {\rm (ET3)}.
\item[{\rm (ET4)}] Let~$\delta\in\mathbb{E}(Z',X)$ and~$\delta'\in\mathbb{E}(X',Y)$ be~$\mathbb{E}$-extensions realized respectively by
\[
X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z'\ \text{ and } \ Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
\]
Then there exist an object~$Y'\in\cat$, a commutative diagram in~$\cat$
\[
\xy
(-18,6)*+{X}="0";
(-6,6)*+{Y}="2";
(6,6)*+{Z'}="4";
(18,6)="6";
%
(-18,-6)*+{X}="10";
(-6,-6)*+{Z}="12";
(6,-6)*+{Y'}="14";
(18,-6)="16";
%
(-6,-18)*+{X'}="22";
(6,-18)*+{X'}="24";
%
(-6,-28)="32";
(6,-28)="34";
%
%
{\ar^{f} "0";"2"};
{\ar^{f'} "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar_{g} "2";"12"};
{\ar^{d} "4";"14"};
%
{\ar^{h} "10";"12"};
{\ar^{h'} "12";"14"};
%
{\ar_{g'} "12";"22"};
{\ar^{e} "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{}|{} "0";"12"};
{\ar@{}|{} "2";"14"};
{\ar@{}|{} "12";"24"};
%
{\ar@{-->}^\delta "4";"6"};
{\ar@{-->}^{\delta''} "14";"16"};
{\ar@{-->}^{\delta'} "22";"32"};
{\ar@{-->}^{f'_\ast \delta'} "24";"34"};
%
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
and an~$\mathbb{E}$-extension~$\delta''\in\mathbb{E}(Y',X)$ realized by~$X\overset{h}{\longrightarrow}Z\overset{h'}{\longrightarrow}Y'$, which satisfy the following compatibilities.
  \begin{enumerate}[(i)]
    \item $Z'\overset{d}{\longrightarrow}Y'\overset{e}{\longrightarrow}X'$ realizes~$f'_\ast\delta'$,
    \item $d^\ast\delta''=\delta$,
    \item $f_\ast\delta''=e^\ast\delta'$. 
  \end{enumerate}
\item[{\rm (ET4)$^{\mathrm{op}}$}] Dual of {\rm (ET4)}.
\end{itemize}
\end{definition}

@@

\begin{lemma}
\label{lemma::shifts of extriangles}
Let~$X\in\cat$ and let
\[
T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \ \ \ T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \ \ \ T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
\]
be extriangles with~$T_0^X,T_1^X\in\tc$.
Then there are extriangles
\[
T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \ \ \ X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
\]
where~$h_X$ is the unique morphism in~$\cat(X,\susp T_1^X)$ satisfying~$(h_X)^\ast\delta_1=\delta_X$ and~$\susp f_X$ is the unique morphism in~$\cat(\susp T_1^X,\susp T_0^X)$ satisfying~$(\susp f_X)^\ast\delta_0 = (f_X)_\ast\delta_1$.
\end{lemma}

@@

\begin{remark}
It follows from the proof of \cref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in \cref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
\[
{\rm (3')} \ \ \ \cat = \tc\ast\susp\tc.
\]
\end{remark}

@@

\begin{proof}
Let~$X\infl Y\defl Z$ be a conflation in~$\cat$.
Fix conflations~$T_1^XÂ \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
By~\cite[Prop.~3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations
\[
\xy
%
(-7,21)*+{T^Z_1}="-12";
(10,21)*+{T^Z_1}="-14";
%
(-24,7)*+{X}="0";
(-7,7)*+{X\oplus T^Z_0}="2";
(10,7)*+{T^Z_0}="4";
%
(-24,-7)*+{X}="10";
(-7,-7)*+{Y}="12";
(10,-7)*+{Z}="14";
%
{\ar@{=} "-12";"-14"};
%
{\ar "-12";"2"};
{\ar "-14";"4"};
%
{\ar "0";"2"};
{\ar "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar "2";"12"};
{\ar "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
%
{\ar@{}|\circlearrowright "-12";"4"};
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
\endxy
\ \ \ \ \ \ \ \
\xy
(-24,21)*+{T^X_1}="0";
(-7,21)*+{B}="2";
(14,21)*+{T^Z_1}="4";
%
(-24,7)*+{T^X_1}="10";
(-7,7)*+{T^X_0\oplus T^Z_0}="12";
(14,7)*+{X\oplus T^Z_0}="14";
%
(-7,-7)*+{Y}="22";
(14,-7)*+{Y}="24";
%
%
{\ar "0";"2"};
{\ar "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar "2";"12"};
{\ar "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
%
{\ar "12";"22"};
{\ar "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
where we have used the fact that~$T_0^Z$ is projective in~$\cat$.
Moreover, the conflation with middle term~$B$ splits, which implies that~$B$ is isomorphic to~$T_1^X\oplus T_1^Z$.
\end{proof}

>>>>

\begin{lemma}
\label{lemm::mesh mutations and meshes}
The set of positive mesh mutations~$(x,x')$ of Definition~\ref{defn::positive mutation} is in bijection with the set~$\meshes$ from~\ref{defn::positive mutation}.
\end{lemma}

\begin{proof}
If~$(x,x')$ is a positive mesh mutation, then~$\{x,x'\}$ is in~$\meshes$.  Indeed, if~$X$ and~$X'$ are the the corresponding objects in~$\cat$.  Then there is an almost-split triangle
\[
X\to E\to X' \to \susp E,
\]
so that~$X' = \tau^{-1}X$.  Moreover, there is a slice of the Auslander--Reiten quiver of~$\cat$ containing~$X$ and all indecomposable direct factors of~$E$.  The direct sum of indecomposable objects in this slice is a cluster-tilting object in which~$X$ is a sink, and mutation at~$X$ gives~$X'$.  Thus~$\{x,x'\}$ is in~$\meshes$.  This gives an injective map from the set of positive mutations to~$\meshes$.

\smallskip
Next, assume that~$\{x,x'\}\in \meshes$ starts in~$x$.  Then there is a cluster-tilting object~$T$ in~$\cat$ having~$X$ as a direct factor, and such that~$X$ is a sink in~$T$ and mutation at~$X$ yields~$X'$.  Since~$X$ is a sink, the mutation triangle starting and ending in~$X$ are
\[
X\to E\to X' \to \susp X \quad \textrm{and} \quad  X' \to 0 \to X \to \susp X'.
\]
Therefore~$X' = \susp^{-1}X = \tau^{-1}X$.  Thus the first triangle is the almost-split triangle starting in~$X$.  Since the pair~$\{x,x'\}$ is not initial, the mutation is a positive mesh mutation.  This gives an injective map from~$\meshes$ to the set of positive mutations. 
\end{proof}

@@

\begin{remark}
Let~$\delta\in\mathbb{E}(Z,X)$ be an~$\mathbb{E}$-extension. By functoriality, any morphisms~$f\in\cat(X,X')$ and~$h\in\cat(Z',Z)$ induce~$\mathbb{E}$-extensions~$\mathbb{E}(Z,f)(\delta)\in\mathbb{E}(Z,X') \text{ and } \mathbb{E}(h,X)(\delta)\in\mathbb{E}(Z',X)$.
For short, we write~$f_\ast\delta$ and~$h^\ast\delta$ instead.
Using those notations, we have, in~$\mathbb{E}(Z',X')$
\[
\mathbb{E}(h,f)(\delta)=h^\ast f_\ast\delta=f_\ast h^\ast\delta.
\]
\end{remark}

@@

\begin{definition}
\label{DefSqEquiv}
Let~$X,Z\in\cat$ be any two objects. Two sequences of morphisms in~$\cat$
\[
X \overset{x}{\longrightarrow}Y\overset{y}{\longrightarrow}Z \text{ and } X\overset{x'}{\longrightarrow}Y'\overset{y'}{\longrightarrow}Z
\]
are said to be \defn{equivalent} if there exists an isomorphism~$g\in\cat(Y,Y')$ such that the following diagram commutes.
\[
\xy
(-20,0)*+{X}="X";
(5,0)*+{}="1";
(0,6)*+{Y}="Y";
(0,-6)*+{Y'}="Y'";
(-5,0)*+{}="2";
(20,0)*+{Z}="Z";
%
{\ar^{x} "X";"Y"};
{\ar^{y} "Y";"Z"};
{\ar_{x^{\prime}} "X";"Y'"};
{\ar_{y^{\prime}} "Y'";"Z"};
%
{\ar^{g}_{\cong} "Y";"Y'"};
%
{\ar@{}|{} "X";"1"};
{\ar@{}|{} "2";"Z"};
\endxy
\]
The equivalence class of~$X \xrightarrow{x} Y \xrightarrow{y} Z$ is denoted by~$[X \xrightarrow{x} Y \xrightarrow{y} Z]$.
\end{definition}

@@

\begin{definition}(\cite[Def.~2.12]{NakaokaPalu})
A triple~$(\cat,\mathbb{E},\mathfrak{s})$ is called an \defn{extriangulated category} if the following holds:
\begin{itemize}
\item[{\rm (ET1)}] $\mathbb{E}:\cat^{\mathrm{op}}\times\cat\to\mathit{Ab}$ is an additive bifunctor;
\item[{\rm (ET2)}] $\mathfrak{s}$ is an additive realization of~$\mathbb{E}$;
\item[{\rm (ET3)}] Let~$\delta\in\mathbb{E}(Z,X)$ and~$\delta'\in\mathbb{E}(Z',X')$ be~$\mathbb{E}$-extensions, respectively realized by~$X\xrightarrow{x}Y\xrightarrow{y}Z$ and~$X'\xrightarrow{x'}Y'\xrightarrow{y'}Z'$. Then, for any commutative square
\[
\xy
(-12,6)*+{X}="0";
(0,6)*+{Y}="2";
(12,6)*+{Z}="4";
%
(-12,-6)*+{X'}="10";
(0,-6)*+{Y'}="12";
(12,-6)*+{Z'}="14";
%
{\ar^{x} "0";"2"};
{\ar^{y} "2";"4"};
%
{\ar_{f} "0";"10"};
{\ar^{g} "2";"12"};
%
{\ar_{x'} "10";"12"};
{\ar_{y'} "12";"14"};
%
{\ar@{}|{} "0";"12"};
%
{\ar@{}|\circlearrowright "0";"12"};
\endxy 
\]
in~$\cat$, there exists a morphism~$(f,h):\delta\to\delta'$ satisfying~$h\circ y=y'\circ g$.
\item[{\rm (ET3)$^{\mathrm{op}}$}] Dual of {\rm (ET3)}.
\item[{\rm (ET4)}] Let~$\delta\in\mathbb{E}(Z',X)$ and~$\delta'\in\mathbb{E}(X',Y)$ be~$\mathbb{E}$-extensions realized respectively by
\[
X\overset{f}{\longrightarrow}Y\overset{f'}{\longrightarrow}Z' \quad\text{and}\quad Y\overset{g}{\longrightarrow}Z\overset{g'}{\longrightarrow}X'.
\]
Then there exist an object~$Y'\in\cat$, a commutative diagram in~$\cat$
\[
\xy
(-18,6)*+{X}="0";
(-6,6)*+{Y}="2";
(6,6)*+{Z'}="4";
(18,6)="6";
%
(-18,-6)*+{X}="10";
(-6,-6)*+{Z}="12";
(6,-6)*+{Y'}="14";
(18,-6)="16";
%
(-6,-18)*+{X'}="22";
(6,-18)*+{X'}="24";
%
(-6,-28)="32";
(6,-28)="34";
%
%
{\ar^{f} "0";"2"};
{\ar^{f'} "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar_{g} "2";"12"};
{\ar^{d} "4";"14"};
%
{\ar^{h} "10";"12"};
{\ar^{h'} "12";"14"};
%
{\ar_{g'} "12";"22"};
{\ar^{e} "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{}|{} "0";"12"};
{\ar@{}|{} "2";"14"};
{\ar@{}|{} "12";"24"};
%
{\ar@{-->}^\delta "4";"6"};
{\ar@{-->}^{\delta''} "14";"16"};
{\ar@{-->}^{\delta'} "22";"32"};
{\ar@{-->}^{f'_\ast \delta'} "24";"34"};
%
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
and an~$\mathbb{E}$-extension~$\delta''\in\mathbb{E}(Y',X)$ realized by~$X\overset{h}{\longrightarrow}Z\overset{h'}{\longrightarrow}Y'$, which satisfy the following compatibilities.
  \begin{enumerate}[(i)]
    \item $Z'\overset{d}{\longrightarrow}Y'\overset{e}{\longrightarrow}X'$ realizes~$f'_\ast\delta'$,
    \item $d^\ast\delta''=\delta$,
    \item $f_\ast\delta''=e^\ast\delta'$. 
  \end{enumerate}
\item[{\rm (ET4)$^{\mathrm{op}}$}] Dual of {\rm (ET4)}.
\end{itemize}
\end{definition}

@@

\begin{lemma}
\label{lemma::shifts of extriangles}
Let~$X\in\cat$ and let
\[
T_1^X\overset{f_X}{\infl} T_0^X\overset{g_X}{\defl} X \overset{\delta_X}{\dashrightarrow}, \quad T_0^X\infl 0\defl \susp T_0^X\overset{\delta_0}{\dashrightarrow}, \quad T_1^X\infl 0\defl \susp T_1^X\overset{\delta_1}{\dashrightarrow}
\]
be extriangles with~$T_0^X,T_1^X\in\tc$.
Then there are extriangles
\[
T_0^X\overset{g_X}{\infl} X \overset{h_X}{\defl} \susp T_1^X \overset{(f_X)_\ast\delta_1}{\dashrightarrow}, \quad X \overset{h_X}{\infl} \susp T_1^X \overset{\susp f_X}{\defl} \susp T_0^X \overset{(g_X)_\ast\delta_0}{\dashrightarrow}
\]
where~$h_X$ is the unique morphism in~$\cat(X,\susp T_1^X)$ satisfying~$(h_X)^\ast\delta_1=\delta_X$ and~$\susp f_X$ is the unique morphism in~$\cat(\susp T_1^X,\susp T_0^X)$ satisfying~$(\susp f_X)^\ast\delta_0 = (f_X)_\ast\delta_1$.
\end{lemma}

@@

\begin{remark}
It follows from the proof of \cref{lemma:: mphs in T are inflations} that conditions (1), (2), (3) in \cref{setting::extricat} are equivalent to conditions (1), (2), (3'), where
\[
{\rm (3')} \quad \cat = \tc\ast\susp\tc.
\]
\end{remark}

@@

\begin{proof}
Let~$X\infl Y\defl Z$ be a conflation in~$\cat$.
Fix conflations~$T_1^XÂ \infl T_0^X \defl X$,~$T_1^Z\infl T_0^Z \defl Z$ with~$T_0^X, T_1^X, T_0^Z, T_1^Z\in\tc$.
By~\cite[Prop.~3.15]{NakaokaPalu} and axiom (ET4)$^{\mathrm{op}}$, there are commutative diagrams of conflations
\[
\xy
%
(-7,21)*+{T^Z_1}="-12";
(10,21)*+{T^Z_1}="-14";
%
(-24,7)*+{X}="0";
(-7,7)*+{X\oplus T^Z_0}="2";
(10,7)*+{T^Z_0}="4";
%
(-24,-7)*+{X}="10";
(-7,-7)*+{Y}="12";
(10,-7)*+{Z}="14";
%
{\ar@{=} "-12";"-14"};
%
{\ar "-12";"2"};
{\ar "-14";"4"};
%
{\ar "0";"2"};
{\ar "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar "2";"12"};
{\ar "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
%
{\ar@{}|\circlearrowright "-12";"4"};
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
\endxy
\quad \quad \ \
\xy
(-24,21)*+{T^X_1}="0";
(-7,21)*+{B}="2";
(14,21)*+{T^Z_1}="4";
%
(-24,7)*+{T^X_1}="10";
(-7,7)*+{T^X_0\oplus T^Z_0}="12";
(14,7)*+{X\oplus T^Z_0}="14";
%
(-7,-7)*+{Y}="22";
(14,-7)*+{Y}="24";
%
%
{\ar "0";"2"};
{\ar "2";"4"};
%
{\ar@{=} "0";"10"};
{\ar "2";"12"};
{\ar "4";"14"};
%
{\ar "10";"12"};
{\ar "12";"14"};
%
{\ar "12";"22"};
{\ar "14";"24"};
%
{\ar@{=} "22";"24"};
%
{\ar@{}|\circlearrowright "0";"12"};
{\ar@{}|\circlearrowright "2";"14"};
{\ar@{}|\circlearrowright "12";"24"};
\endxy
\]
where we have used the fact that~$T_0^Z$ is projective in~$\cat$.
Moreover, the conflation with middle term~$B$ splits, which implies that~$B$ is isomorphic to~$T_1^X\oplus T_1^Z$.
\end{proof}
